---
title: "002_compile_prep_check_data_kibi"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: today()
output: pdf_document
---

# Data

Downloaded _prepared.Rdata from share point ....


```{r setup, include=FALSE}
library(data.table)
library(fishPiCodes)	
library(foreign) 
library(dplyr)
library(knitr)
library(lubridate)
library(ggplot2)

data_dir <- "Q:/dfad/users/kibi/data/RCG/from_share_point/"
output_dir <- "Q:/mynd/kibi/projects_wks_wgs/RCG_SPF_Baltic/RCG_BA/SamplingPlans/SmallPelagics/output/"

knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F,
  error = F,
  comment = F,
  fig.width = 16, fig.height = 8, fig.path = output_dir, dpi = 900, dev = 'jpeg', results = 'asis')

#setwd("SamplingPlans/SmallPelagics")
```

## Nuno's check

```{r, include = F}

# Code from 002_compile_and_prepare_countries_data - created by Nuno


library(data.table)		
		
# ========================
# reads in data
# ========================
 
 for(ctry in c("DEU","DNK","EST","FIN","LTU","LVA","POL","SWE")) 
	{
	load(paste(data_dir, ctry, "_prepared.Rdata", sep=""))
	}

  dt_deu <- select(dt_deu, -spp_Code_aphia)	

	dt1<-bind_rows(dt_deu, dt_dnk, dt_est, dt_fin, dt_ltu, dt_lva, dt_pol, dt_swe)

# ========================	
# some additional variables
# ========================
	 
	# Year of landing
	dt1$year<-format(as.Date(dt1$landDate), format="%Y") 

	# Month of landing
	dt1$month<-factor(as.numeric(format(as.Date(dt1$landDate), format="%m")), levels=1:12) 
	
	# gearType: active or passive
	active_gears<-c('OTB','PTM','PTB','SDN','OTM','PS_','SB_','OTT')
	passive_gears<-unique(substring(dt1$foCatEu6,1,3))[!unique(substring(dt1$foCatEu6,1,3)) %in% active_gears]; passive_gears
	dt1$gearType<-NA
	dt1$gearType[substring(dt1$foCatEu6,1,3) %in% active_gears]<-"Active"
	dt1$gearType[!substring(dt1$foCatEu6,1,3) %in% active_gears]<-"Passive"

	
# ========================
# some additional checks and fixes on data
# ======================== 
 
	# issues on unique(vslLenCls) per trip		
		nrow(dt1[, length(unique(vslLenCls)), fishTripId][V1>1,])
	# issues on unique(vslLenCls) per vessel		
		nrow(dt1[, length(unique(vslLenCls)), list(year, vslId, gearType)][V1>1,])
		dt1[, length(unique(vslLenCls)), list(year, vslId, gearType)][V1>1,]
			# all passive - will be outside of sampling frame so ok.
	# issues on unique(depDate) per trip		
		nrow(dt1[, length(unique(depLoc)), fishTripId][V1>1,])
	# issues on unique(depLoc) per trip		
		nrow(dt1[, length(unique(depLoc)), fishTripId][V1>1,])
	# issues on unique(landDate) per trip		
		nrow(dt1[, length(unique(landDate)), fishTripId][V1>1,])
	# issues on unique(landLoc) per trip		
		nrow(dt1[, length(unique(landLoc)), fishTripId][V1>1,])
		dt1[, length(unique(landLoc)), list(fishTripId, gearType)][V1>1,]
	# slight fix of 4 nephrops trips (for consistency only)
		dt1$landLoc[dt1$fishTripId == "DNK20171121275"] <- "DKQSB"
		dt1$landLoc[dt1$fishTripId == "DNK20180816126"] <- "DKQSB"
		dt1$landLoc[dt1$fishTripId == "DNK20180816054"] <- "DKQSB"
		dt1$landLoc[dt1$fishTripId == "DNK20180815955"] <- "DKQSB"
		dt1[, length(unique(landLoc)), list(fishTripId, gearType)][V1>1,]
			# all remainder are passive - will be outside of sampling frame so ok.
	# issues on unique(sppCode) per sppName		
		nrow(dt1[, length(unique(sppCode)), sppName][V1>1,])
	# issues on unique(sppName) per sppCode		
		nrow(dt1[, length(unique(sppName)), sppCode][V1>1,])
			dt1$sppName[dt1$sppCode==127149]<-"Scophthalmus maximus"	
			dt1$sppName[dt1$sppCode==10194]<-"Actinopterygii"	
			nrow(dt1[, length(unique(sppName)), sppCode][V1>1,])
	# duplicates
			sum(duplicated(dt1))		
			dt1[duplicated(dt1) | duplicated(dt1, fromLast=T),]
			table(dt1[duplicated(dt1) | duplicated(dt1, fromLast=T),]$vslFlgCtry)
			# fix: elimination
			dt1<-dt1[!duplicated(dt1),]	
	# ID duplicates
		dt1[,.N, list(year, fishTripId, depDate, depLoc, landDate, landLoc, rect, area,foCatEu6, sppCode, sppName, landCat)][N>1,]
		# fix by aggregation
			dt1<-dt1[,list(landWt=sum(landWt)), list(year, vslFlgCtry,vslId,vslLenCls,fishTripId,depDate,depLoc,landDate,landLoc,rect,area,gearType,foCatEu6,sppCode,sppName,landCat)] 

saveRDS(dt1, paste0(data_dir, "bs_spf_compiled.rds"))
```

## More checks

```{r combine_trip_data, include = F}

dt1$landDate <- as.Date(dt1$landDate)

#correction of area 28

dt1 <- mutate(dt1, area = ifelse(!(vslFlgCtry %in% c("LVA", "EST")) & area == "27.3.d.28", "27.3.d.28.2", area))

dt1 <- mutate(dt1, area = ifelse(sppName == "Sprattus sprattus" &  area %in% c("27.3.d.28.1", "27.3.d.28.2"), "27.3.d.28", area))

#Add stock
#Add sppFAO - this is needed for the stock function
data(ASFIS)

FAO <- distinct(ASFIS, X3A_CODE, Scientific_name)
FAO <- rename(FAO, sppFAO = X3A_CODE, sppName = Scientific_name)

dt2 <- left_join(dt1, FAO) #More lines created with this join

source("Q:/mynd/kibi/functions/GetStock_v1_1.R")

dt2 <- GetStock(dt2)

no_stock <- summarise(group_by(filter(dt2, stock == "no.defined.stock" & sppName %in% c("Clupea harengus", "Sprattus sprattus")), sppName, area, year, vslFlgCtry), landWt_ton = sum(landWt/1000))


saveRDS(dt2, paste(data_dir, "df_bs_spf.rds", sep = ""))

dt_spf <- filter(dt2, sppName %in% c("Sprattus sprattus", "Clupea harengus"))
```


```{r read_rdb, include = F}

```

## Area 27.3.d.28

Important for herring

*Do we need to correct or can we assume?*

Guess it is only Estonia and Latvia fishing in the Gulf of Riga - *correct?*

Assuming that 28.2, when not Latvia | Estonia

```{r area_28}

dt_28 <- filter(dt_spf, substr(area, 1, 9) == "27.3.d.28" & sppName == "Clupea harengus")

kable(summarise(group_by(dt_28, vslFlgCtry, area, sppName), tons = sum(landWt/1000, na.rm = T)), caption = "Area 27.3.d.28 with or without .1 | .2")

```

## Landing categories

*How to group / re-code?*

```{r landCat}
kable(summarise(group_by(dt_spf, vslFlgCtry, sppName, landCat), tons = sum(landWt/1000, na.rm = T)), caption = "Landing categories")
```


## Missing dates
### landDate

```{r mis_landdates}

dt_depdates <- filter(dt_spf, landDate %in% c("", "NA", NA))

mis <- summarise(group_by(dt_depdates, vslFlgCtry, sppName), tons = sum(landWt/1000, na.rm = T))
total <- summarise(group_by(dt_spf, vslFlgCtry, sppName), tons_total = sum(landWt/1000, na.rm = T))
mis_2 <- mutate(left_join(total, mis), pct_mis = (tons/tons_total)*100)

kable(mis_2, caption = "Missing landDate")

```

### depDate

```{r mis_depdates}

dt_depdates <- filter(dt_spf, depDate %in% c("", "NA", NA))

mis <- summarise(group_by(dt_depdates, vslFlgCtry, sppName), tons = sum(landWt/1000, na.rm = T))
total <- summarise(group_by(dt_spf, vslFlgCtry, sppName), tons_total = sum(landWt/1000, na.rm = T))
mis_2 <- mutate(left_join(total, mis), pct_mis = (tons/tons_total)*100)

kable(mis_2, caption = "Missing depDate")

```


### both dates 

```{r mis_dates}

dt_depdates <- filter(dt_spf, depDate %in% c("", "NA", NA) & landDate %in% c("", "NA", NA))

mis <- summarise(group_by(dt_depdates, vslFlgCtry, sppName), tons = sum(landWt/1000, na.rm = T))
total <- summarise(group_by(dt_spf, vslFlgCtry, sppName), tons_total = sum(landWt/1000, na.rm = T))
mis_2 <- mutate(left_join(total, mis), pct_mis = (tons/tons_total)*100)

kable(mis_2, caption = "Missing both Date")

```

## Missing or incorrect location
### landLoc

```{r}
data("UNLOCODE")
dt_loc <- filter(dt_spf, !(landLoc %in% UNLOCODE$loCode))

mis <- summarise(group_by(dt_loc, vslFlgCtry, sppName), tons = sum(landWt/1000, na.rm = T))
total <- summarise(group_by(dt_spf, vslFlgCtry, sppName), tons_total = sum(landWt/1000, na.rm = T))
mis_2 <- mutate(left_join(total, mis), pct_mis = (tons/tons_total)*100)

kable(mis_2, caption = "Missing landLoc")

```


### depLoc

```{r}
data("UNLOCODE")
dt_loc <- filter(dt_spf, !(depLoc %in% UNLOCODE$loCode))

mis <- summarise(group_by(dt_loc, vslFlgCtry, sppName), tons = sum(landWt/1000, na.rm = T))
total <- summarise(group_by(dt_spf, vslFlgCtry, sppName), tons_total = sum(landWt/1000, na.rm = T))
mis_2 <- mutate(left_join(total, mis), pct_mis = (tons/tons_total)*100)

kable(mis_2, caption = "Missing depLoc")

```


### Both loc

```{r}
data("UNLOCODE")
dt_loc <- filter(dt_spf, !(landLoc %in% UNLOCODE$loCode) & !(depLoc %in% UNLOCODE$loCode))

mis <- summarise(group_by(dt_loc, vslFlgCtry, sppName), tons = sum(landWt/1000, na.rm = T))
total <- summarise(group_by(dt_spf, vslFlgCtry, sppName), tons_total = sum(landWt/1000, na.rm = T))
mis_2 <- mutate(left_join(total, mis), pct_mis = (tons/tons_total)*100)

kable(mis_2, caption = "Missing both Loc")

```

## Overall landings

A table for checking against advice sheets


```{r overall_lan}

#kable(summarise(group_by(dt_spf, year, vslFlgCtry, area, sppName), tons = sum(landWt/1000, na.rm = T)), caption = "Overall landings")

```

# Analyses
## Target population

```{r target}

dt_sum <- filter(summarise(group_by(dt2, fishTripId, sppName), ton = sum(landWt/1000, na.rm = T)), ton > 0)

dt_sum_1 <- mutate(dt_sum, spp = ifelse(sppName %in% c("Sprattus sprattus", "Clupea harengus"), "HER+SPR", "other"))

dt_sum_2 <- filter(summarise(group_by(dt_sum_1, fishTripId, spp), ton = sum(ton, na.rm = T)), ton > 0)

dt_tot <- summarise(group_by(dt_sum_2, fishTripId), ton_tot = sum(ton, na.rm = T))

dt_pct <- mutate(left_join(dt_sum_2, dt_tot), pct_her_spr_trip = (ton/ton_tot)*100)

trips_her_spr <- mutate(arrange(filter(dt_pct, spp == "HER+SPR"), pct_her_spr_trip, ton), cum = cumsum(ton))


```

*When are trip targeting sprat or herring?*

Total number of trips (all species); `r length(unique(dt_sum$fishTripId))`

Total landings of herring and sprat (tons): `r as.character(round(sum(trips_her_spr$ton), digits = 0))`

Total number of trips (more than 80 pct of sprat or herring); `r length(unique(dt_pct$fishTripId[dt_pct$pct_her_spr_trip > 80]))`

Total landings of herring and sprat (more than 80 pct of sprat or herring): `r as.character(round(sum(trips_her_spr$ton[trips_her_spr$pct_her_spr_trip > 80]), digits = 0))`

Total number of trips (more than 90 pct of sprat or herring); `r length(unique(dt_pct$fishTripId[dt_pct$pct_her_spr_trip > 90]))`

Total landings of herring and sprat (more than 90 pct of sprat or herring): `r as.character(round(sum(trips_her_spr$ton[trips_her_spr$pct_her_spr_trip > 90]), digits = 0))`


```{r, fig.cap = "xx"}

ggplot(trips_her_spr, aes(x = pct_her_spr_trip)) +
  geom_histogram(binwidth = 1) + 
  geom_vline(xintercept = 79.5, color = "red") +
  labs(title = "Number of trips per pct of herring and sprat", subtitle = "Red line: 80 pct. of herring or sprat", 
       y = "Number of trips", x = "Pct. herring and sprat on a trip")

```

```{r, fig.cap = "xx"}

ggplot(trips_her_spr, aes(x = pct_her_spr_trip, y = ton)) +
  geom_bar(stat = "identity", width = 1) + 
  geom_line(aes(x = pct_her_spr_trip, y = cumsum(ton)), col = "red") +
  labs(title = "Tons per pct of herring and sprat", subtitle = "Red line: accumulated landings", 
       y = "Tons", x = "Pct. herring and sprat on a trip")

```



# Stock

```{r}
kable(summarise(group_by(dt_spf, year, stock), ton = sum(landWt/1000)))
```



```{r}
kable(summarise(group_by(dt_spf, year, vslFlgCtry, stock), ton = sum(landWt/1000)))
```

