---
title: "004_locations"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: \today
output: pdf_document
---

# Finding the locations - both fleets (active & passive)

Most important landing location per stock in 2018 - *where to set the treshold for that?*

Relevant figures can be found in 004_RCG_BS_SPF_locations.xlsx


```{r setup, include=FALSE}
library(data.table)
library(fishPiCodes)	
library(foreign) 
library(dplyr)
library(knitr)
library(lubridate)
library(ggplot2)
library(openxlsx)

Sys.setenv(R_ZIPCMD = "C:/Rtools/bin/zip")
options(scipen = 9999,
        digits = 8,
        max.print = 100000)

data_dir <- "Q:/dfad/users/kibi/data/RCG/from_share_point/"
output_dir <- "Q:/mynd/kibi/projects_wks_wgs/RCG_SPF_Baltic/RCG_BA/SamplingPlans/SmallPelagics/output/"

knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F,
  error = F,
  comment = F)

#setwd("SamplingPlans/SmallPelagics")
```

```{r load_data, include = F}

dat <- readRDS(paste(data_dir, "df_bs_spf.rds", sep = ""))

dt_spf <- filter(dat, sppName %in% c("Sprattus sprattus", "Clupea harengus") & year == 2018)
```

```{r}
kable(summarise(group_by(dt_spf, year, stock), tons = sum(landWt/1000)))
```

```{r loc_stock}

loc <- arrange(summarise(group_by(dt_spf, stock, landLoc), tons = sum(landWt/1000)), stock, -tons)

loc_cum <- mutate(loc, cumsum = cumsum(tons), cumpct = (cumsum(tons)/sum(tons))*100, pct = (tons/sum(tons))*100)

```

## Setting a treshold

Total number of locations: `r length(unique(loc_cum$landLoc))`

Total number of unique locations (treshold 95% accumulated per stock): `r nrow(distinct(filter(ungroup(loc_cum), cumpct <= 95 | pct >= 95), landLoc))`

Total number of unique locations (treshold 90% accumulated per stock): `r nrow(distinct(filter(ungroup(loc_cum), cumpct <= 90 | pct >= 90), landLoc))`

Total number of unique locations (treshold 85% accumulated per stock): `r nrow(distinct(filter(ungroup(loc_cum), cumpct <= 85 | pct >= 85), landLoc))`


```{r, include = F}

#Create a workbook with all the options

wb <- createWorkbook("RCG_BS_SPF_locations")
addWorksheet(wb, "treshold_85")
addWorksheet(wb, "treshold_90")
addWorksheet(wb, "treshold_95")
addWorksheet(wb, "all")
addWorksheet(wb, "all_per_stock")


all <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 100 |
                        pct >= 100), landLoc),
      "type_of_loc_eg_factory_auction_" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )
t_85 <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 85 |
                        pct >= 85), landLoc),
      "type_of_loc" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )
t_90 <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 90 |
                        pct >= 90), landLoc),
      "type_of_loc" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )
t_95 <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 95 |
                        pct >= 95), landLoc),
      "type_of_loc" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )


writeData(wb, sheet = "treshold_85", t_85)
writeData(wb, sheet = "treshold_90", t_90)
writeData(wb, sheet = "treshold_95", t_95)
writeData(wb, sheet = "all", all)
writeData(wb, sheet = "all_per_stock", loc_cum)
saveWorkbook(wb, paste(output_dir, "004_RCG_BS_SPF_locations.xlsx", sep = ""), overwrite = TRUE)




```


# Finding the locations - active only

Most important landing location per stock in 2018 - *where to set the treshold for that?*

Relevant figures can be found in 004_RCG_BS_SPF_locations_active.xlsx

```{r load_data_active, include = F}

dat <- readRDS(paste(data_dir, "df_bs_spf.rds", sep = ""))

dt_spf <- filter(dat, sppName %in% c("Sprattus sprattus", "Clupea harengus") & year == 2018 & gearType == "Active")
```

```{r}
kable(summarise(group_by(dt_spf, year, stock), tons = sum(landWt/1000)))
```

```{r loc_stock_active}

loc <- arrange(summarise(group_by(dt_spf, stock, landLoc), tons = sum(landWt/1000)), stock, -tons)

loc_cum <- mutate(loc, cumsum = cumsum(tons), cumpct = (cumsum(tons)/sum(tons))*100, pct = (tons/sum(tons))*100)

```

## Setting a treshold

Total number of locations: `r length(unique(loc_cum$landLoc))`

Total number of unique locations (treshold 95% accumulated per stock): `r nrow(distinct(filter(ungroup(loc_cum), cumpct <= 95 | pct >= 95), landLoc))`

Total number of unique locations (treshold 90% accumulated per stock): `r nrow(distinct(filter(ungroup(loc_cum), cumpct <= 90 | pct >= 90), landLoc))`

Total number of unique locations (treshold 85% accumulated per stock): `r nrow(distinct(filter(ungroup(loc_cum), cumpct <= 85 | pct >= 85), landLoc))`


```{r, include = F}

#Create a workbook with all the options

wb <- createWorkbook("RCG_BS_SPF_locations_active")
addWorksheet(wb, "treshold_85")
addWorksheet(wb, "treshold_90")
addWorksheet(wb, "treshold_95")
addWorksheet(wb, "all")
addWorksheet(wb, "all_per_stock")


all <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 100 |
                        pct >= 100), landLoc),
      "type_of_loc_eg_factory_auction_" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )
t_85 <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 85 |
                        pct >= 85), landLoc),
      "type_of_loc" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )
t_90 <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 90 |
                        pct >= 90), landLoc),
      "type_of_loc" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )
t_95 <-
  arrange(
    mutate(
      distinct(filter(ungroup(loc_cum), cumpct <= 95 |
                        pct >= 95), landLoc),
      "type_of_loc" = "",
      "type_of_landings" = "",
      "possible_to_sample" = "",
      "Presently_sampled" = ""
    ),
    landLoc
  )


writeData(wb, sheet = "treshold_85", t_85)
writeData(wb, sheet = "treshold_90", t_90)
writeData(wb, sheet = "treshold_95", t_95)
writeData(wb, sheet = "all", all)
writeData(wb, sheet = "all_per_stock", loc_cum)
saveWorkbook(wb, paste(output_dir, "004_RCG_BS_SPF_locations_active.xlsx", sep = ""), overwrite = TRUE)




```


