---
title: "007_read_and_prep_sample_data"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "06/06/2019"
output: pdf_document
---


```{r setup, include=FALSE}

library(fishPiCodes)	
library(dplyr)
library(knitr)
library(lubridate)
library(ggplot2)

data_dir <- "Q:/dfad/users/kibi/data/RCG/from_share_point/"

knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F,
  error = F,
  comment = F)

#setwd("SamplingPlans/SmallPelagics")
```

# Data

Only selecting samples with heernig | sprat in area 27.3

```{r read_data, include = F, eval = T}

ca_spf <- readRDS(paste(data_dir, "ca_bs_spf.rds", sep = ""))

tr <- readRDS(paste(data_dir, "tr_bs_spf.rds", sep = ""))

trca <- right_join(tr, ca_spf)

```

# Number of trips - overall

## Trying to count with CA only

### All CA records

```{r}

kable(summarise(group_by(ca_spf, Year), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(ca_spf, Year, Species), no_trips = length(unique(CS_TripId))))

```


### Only aged

That worked really well in HAWG - and overall the number of samples are more or less the same, so sticking with that one

```{r}

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, Species), no_trips = length(unique(CS_TripId))))

```

## Output for checking against other sources

Checked figures for her.27.20-24 against figures submitted to HAWG

Number of samples 2017: 150

Number of samples 2018: 132

So quite close ....

Downloaded the WGBFAS report from 2018, so just need to check - at a glance there a way more samples in the report, than in the RDB. Especially Poland seems off.

*This could be due to the fact that not all samples are aged - to be checked*

*Could also check against table 1C*

```{r}

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, stock), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, stock,  SamplingCountry), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, stock, area, SamplingCountry), no_trips = length(unique(CS_TripId))))


```

## A lot of counts

```{r}

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry, FlagCountry), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry, LandingCountry), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry, Species), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry, stock), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, LandingCategory), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry, LandingCategory), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingType), no_trips = length(unique(CS_TripId))))

kable(summarise(group_by(filter(ca_spf, !(is.na(Age))), Year, SamplingCountry, SamplingType), no_trips = length(unique(CS_TripId))))
```

# Number of trips per vessel length

VesselLengthCategory is missing for some of the Danish samples. Denmark don't upload for foreign vessels. Not sure why the Danish ones end up empty - *check*

```{r}

kable(arrange(summarise(group_by(filter(trca, !(is.na(Age))), SamplingCountry, VesselLengthCategory), no_trips = length(unique(CS_TripId))), VesselLengthCategory))

```

# TODO

Number of trips per metier - if possible to join directly

Number of lengths, number of ages

Include some of the plot from HAWG
