---
title: "008_compare_magic_numbers"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "06/06/2019"
output: pdf_document
---

# Aim

See if the sample data in the RDB can be use for simulating biological stuff

Comparing figures from the RDB with the ones in the AWG reports (HAWG and WGBFAS, 2018)


```{r setup, include=FALSE}

library(fishPiCodes)	
library(dplyr)
library(knitr)
library(lubridate)
library(ggplot2)
library(readxl)

data_dir <- "Q:/dfad/users/kibi/data/RCG/from_share_point/"

knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F,
  error = F,
  comment = F)

#setwd("SamplingPlans/SmallPelagics")
```

# Data

Only selecting samples with herring | sprat in area 27.3

```{r read_data, include = F, eval = T}

ca_spf <- readRDS(paste(data_dir, "ca_bs_spf.rds", sep = ""))
hh <- readRDS(paste(data_dir, "hh_bs_spf.rds", sep = ""))

tr <- readRDS(paste(data_dir, "tr_bs_spf.rds", sep = ""))

trca <- right_join(tr, ca_spf)

# With age

ca_age <- filter(ca_spf, !(is.na(Age)))

trip_ids_age <- unique(ca_age$CS_TripId)

tr_age <- filter(tr, CS_TripId %in% trip_ids_age)

hh_age <- filter(hh, CS_TripId %in% trip_ids_age)

trhh_age <- inner_join(tr_age, hh_age)

# AWG figures

awg <- read_xlsx("Q:/mynd/RCM/RCG_BA/SamplingPlans/SmallPelagics/ref/awg_figures_2017.xlsx", sheet = 1)

# Correct countries

awg <- mutate(awg, SamplingCountry = ifelse(ctry == "Denmark", "DNK",
                                      ifelse(ctry == "Germany", "DEU",
                                       ifelse(ctry == "Estonia", "EST",
                                        ifelse(ctry == "Finland", "FIN",
                                         ifelse(ctry == "Latvia", "LVA",
                                          ifelse(ctry == "Lithuania", "LTU",
                                           ifelse(ctry == "Poland", "POL",
                                            ifelse(ctry == "Sweden", "SWE",
                                             ifelse(ctry == "Russia", "RUS",
                                              ifelse(ctry == "Faroe Islands", "FRO",
                                                     ifelse(ctry == "Norway", "NOR", NA))))))))))),
              samples = ifelse(is.na(samples), samples_ages, samples))

awg <- filter(awg, !(SamplingCountry %in% c("RUS","FRO","NOR")))

# AR figures


```


# Number samples - RDB vs. AWG

Diff mainly driven by Poland and Finland. 

THe figures in the Polish AR seems closer to the ones in the RDB.

```{r, include = F}

no_samples_rdb <- summarise(group_by(filter(ca_age, Year == 2017), Year, stock, SamplingCountry), no_samples_rdb = length(unique(CS_TripId)))

no_samples_awg <- summarise(group_by(awg, stock, SamplingCountry), no_samples_awg = sum(samples, na.rm = T))

comp_samples_rdb_awg <- mutate(full_join(no_samples_rdb, no_samples_awg), diff_samples = no_samples_awg - no_samples_rdb)
```

```{r}
kable(arrange(comp_samples_rdb_awg, SamplingCountry, stock))
```


# Number ages - RDB vs. AWG

Diff mainly driven by Latvia and Poland

```{r, include = F}

no_aged_rdb <- summarise(group_by(filter(ca_age, Year == 2017), Year, stock, SamplingCountry), no_aged_rdb = length(unique(CS_SMAWLId)))

no_aged_awg <- summarise(group_by(awg, stock, SamplingCountry), no_aged_awg = sum(ages, na.rm = T))

comp_age_rdb_awg <- mutate(full_join(no_aged_rdb, no_aged_awg), diff_aged = no_aged_awg-no_aged_rdb)
```

```{r}
kable(arrange(comp_age_rdb_awg, SamplingCountry, stock))
```

```{r}
combined <- arrange(full_join(comp_samples_rdb_awg, comp_age_rdb_awg), stock)
```


# Without country

# Number samples - RDB vs. AWG

```{r, include = F}

no_samples_rdb <- summarise(group_by(filter(ca_age, Year == 2017), Year, stock), no_samples_rdb = length(unique(CS_TripId)))

no_samples_awg <- summarise(group_by(awg, stock), no_samples_awg = sum(samples, na.rm = T))

comp_samples_rdb_awg <- mutate(full_join(no_samples_rdb, no_samples_awg), diff_samples = no_samples_awg - no_samples_rdb)
```

```{r}
kable(arrange(comp_samples_rdb_awg, stock))
```


# Number ages - RDB vs. AWG

```{r, include = F}

no_aged_rdb <- summarise(group_by(filter(ca_age, Year == 2017), Year, stock), no_aged_rdb = length(unique(CS_SMAWLId)))

no_aged_awg <- summarise(group_by(awg, stock), no_aged_awg = sum(ages, na.rm = T))

comp_age_rdb_awg <- mutate(full_join(no_aged_rdb, no_aged_awg), diff_aged = no_aged_awg-no_aged_rdb)
```

```{r}
kable(arrange(comp_age_rdb_awg, stock))
```

```{r}
combined <- arrange(full_join(comp_samples_rdb_awg, comp_age_rdb_awg), stock)
```